Malacology: A Programmable Storage System

### 2016-10-21 paper/paper.tex
paper: add capdelay/quota figure
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\title{Malacology: A Programmable Storage System}
\authorinfo{Paper ID: 123}
           {Total Page: 12}
\date{}
\begin{document}

@@

\begin{figure}[tb]
\centering
\includegraphics{figures/overview.png}
\caption{Scalable storage systems consist of storage daemons which store data
fragments, monitor daemons that maintain cluster state, and service-specific
daemons such as file system metadata servers. Malacology enables the
programmability of internal abstractions (indicated by bold arrows) in order to
re-use and compose existing subsystems.  With Malacology, we add two new
services, ZLog and Mantle, that sit alongside the traditional user-facing APIs
(file, block, and object) in the storage stack.  \label{fig:overview}}
\end{figure}

@@

\begin{table}[ht]
\centering
  \begin{tabular}{l|l|l}
    Category & Example & \# \\ \hline
    Logging  & Geographically distribute replicas & 11 \\ \hdashline
    Metadata & Snapshots in the block device OR  & \multirow{2}{*}{74} \\
    Management & Scan extents for file system repair & \\ \hdashline
    Locking  & Grants clients exclusive access & 6 \\ \hdashline
    Other & Garbage collection, reference counting  & 4\\
\end{tabular}
\caption{A variety of RADOS object storage classes exist to expose interfaces
    to applications. \# is the number of methods that use these categories.
}
\label{table:objclasses}
\end{table}

@@

\section{Malacology}
\label{sec:malacology}

@@

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-modes.png}
\caption{The client and proxy balancing modes work well for migrating
sequencers to alleviate overloaded servers. Client mode migrates the sequencer
and clients start sending requests to the new server. Proxy mode migrates the
sequencer but clients continue sending their requests to the first server.
``Half"/``Full" indicate the size of the migration units (discussed in
Section~\ref{sec:feature-migration-units}).}\label{fig:mantle-modes}
\end{figure}

@@

\noindent\textbf{The Malacology Approach:} pull load balancing out of the
storage system to balance sequencers across a cluster. Compared to putting all
sequencers on the same server, load balancing a sequencer using proxy mode
shows a 1.8\(\times\) throughput improvement.\\

@@

Programmable storage is a viable method for eliminating duplication of complex
error prone software that are used as workarounds for storage system
deficiencies. However, this duplication has real-world problems related to
reliability. We propose that system expose their services in a safe way
allowing application developers to customize system behavior to meet their
needs while not sacrificing correctness.

We are intending to pursue this work towards the goal of constructing a set of
customization points that allow a wide variety of storage system services to be
configured on-the-fly in existing systems. This work is one point along that
path in which we have looked at targeting special-purpose storage systems.
Ultimately we want to utilize declarative methods for expressing new services.

>>>>

\title{Malacology: A Programmable Storage System}
\authorinfo{Paper ID: 165}
           {Total Page: 14}
\date{}
\begin{document}

@@

\begin{figure}[tb]
\centering
\includegraphics{figures/overview.png}
\caption{Scalable storage systems consist of storage daemons which store data
fragments, monitor daemons (M) that maintain cluster state, and service-specific
daemons such as file system metadata servers. Malacology enables the
programmability of internal abstractions (indicated by bold arrows) in order to
re-use and compose existing subsystems.  With Malacology, we add two new
services, ZLog and Mantle, that sit alongside the traditional user-facing APIs
(file, block, and object) in the storage stack.  \label{fig:overview}}
\end{figure}

@@

\begin{table}[ht]
\centering
  \begin{tabular}{l|l|l}
    Category & Example & \# \\ \hline
    Logging  & Geographically distribute replicas & 11 \\ \hdashline
    Metadata & Snapshots in the block device OR  & \multirow{2}{*}{74} \\
    Management & Scan extents for file system repair & \\ \hdashline
    Locking  & Grants clients exclusive access & 6 \\ \hdashline
    Other & Garbage collection, reference counting  & 4\\
\end{tabular}
\caption{A variety of object storage classes exist to expose interfaces
    to applications. \# is the number of methods that use these categories.
}
\label{table:objclasses}
\end{table}

@@

\section{Malacology: A Programmable Storage System}
\label{sec:malacology}

@@

\begin{figure}[h]
\centering
\includegraphics{figures/capdelay-quota-behavior-a.png}
\includegraphics{figures/capdelay-quota-behavior-b.png}
\includegraphics{figures/capdelay-quota-behavior-c.png}
\caption{ Each dot in these graphs is an individual request and they are spread
randomly along the \(y\) axis. The default behavior (``None") shows
unpredictable performance, ``delay" lets each client hold the lease longer, and
``quota" gives each client the lease for a certain number of operations. Delay
improves latency and fairness while quota maximizes throughput.}
\label{fig:capdelay-quota-behavior}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-modes.png}
\caption{The client and proxy balancing modes work well for migrating
sequencers to alleviate overloaded servers. Client mode migrates the sequencer
and clients start sending requests to the new server. Proxy mode migrates the
sequencer but clients continue sending their requests to the first server.
``Half" is the size of the migration units (discussed in
Section~\ref{sec:feature-migration-units}).}\label{fig:mantle-modes}
\end{figure}

@@

\noindent\textbf{Malacology pulls} the load balancing out of the storage system
to balance sequencers across a cluster. Compared to putting all sequencers on
the same server, load balancing a sequencer using the proxy mode shows a
1.8\(\times\) throughput improvement.\\

@@

Programmable storage is a viable method for eliminating duplication of complex
error prone software that are used as workarounds for storage system
deficiencies. However, this duplication has real-world problems related to
reliability. We propose that systems expose their services in a safe way
allowing application developers to customize system behavior to meet their
needs while not sacrificing correctness. To illustrate the benefits of this
approach we presented Malacology, a programmable storage system that
facilitates the construction of new services by re-purposing existing subsystem
abstractions of the storage stack.

Future work will focus on constructing more interfaces to support a wide
variety of storage system services that can be configured on-the-fly in existing
systems. This work is one point along that path to producing general-purpose
storage systems that can
target  special-purpose applications.  Ultimately we want to utilize
declarative methods for expressing new services.
